### 2023-10-21 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

\textcolor{blue}
{For a vesicle in free space, tank-treading is often associated with a steady shape and a constant tangential speed along the membrane.
For a vesicle going through dynamic deformation in strong confinement, we provide a criterion for a transient tank-treading membrane 
by first calculating
%Here we described the criterion for determining if a vesicle is tank-treading: we first calculate 
the average, maximum, and minimum tangential velocities over all
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative spreads are
plotted in the bottom row of Figure~\ref{fig:lubricationComposite}. The
average tangential velocities are $-1.00 \times 10^{-1}$ for the stiff
single-component vesicle, $3.31 \times 10^{-2}$ for the floppy
single-component vesicle, and $-8.48 \times 10^{-1}$ for the
multicomponent vesicle. The difference of the maximum and minimum
velocities relative to the average tangential velocities is $1.2\%$ for
the stiff single-component vesicle, $12\%$ for the multicomponent
vesicle, and over $300\%$ for the floppy single-component vesicle.
Therefore, we classify the stiff single-component and multicomponent
vesicles as tank treading, while the floppy single-component is not tank
treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.

>>>>

\textcolor{blue}
{For a vesicle in free space, tank-treading is associated with a steady membrane shape and a constant tangential speed along the membrane.
For a vesicle in strong confinement going through dynamic deformation, we provide a criterion for a transient tank-treading membrane 
by first calculating
%Here we described the criterion for determining if a vesicle is tank-treading: we first calculate 
the average, maximum, and minimum tangential velocities over all
Lagrangian points when the vesicle's center of mass is in the interval
$[4,10]$. If the difference of the maximum and minimum tangential
velocities is within 15\% of the average tangential velocity, we
characterize the vesicle as tank-treading. These relative spreads are
plotted in the bottom row of Figure~\ref{fig:lubricationComposite}. The
average tangential velocities are $-1.00 \times 10^{-1}$ for the stiff
single-component vesicle, $3.31 \times 10^{-2}$ for the floppy
single-component vesicle, and $-8.48 \times 10^{-1}$ for the
multicomponent vesicle. The difference of the maximum and minimum
velocities relative to the average tangential velocities is $1.2\%$ for
the stiff single-component vesicle, $12\%$ for the multicomponent
vesicle, and over $300\%$ for the floppy single-component vesicle.
Therefore, we classify the stiff single-component and multicomponent
vesicles as tank treading, while the floppy single-component is not tank
treading.}
%The stiff single-component and multicomponent vesicles are
%clearly tank treading.
